Metrics

### 2023-11-16 manuscript/manuscript.tex
Fin csmf acc metric

\title[Article Title]{Article Title}

@@

\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}

@@

\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

>>>>

\title[Automatic Cause of Death Assignment from Narratives using ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Narratives using ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022}

@@

\author*[1]{\fnm{Richard} \sur{Wen}}\email{richard.wen@unityhealth.to}

@@

\affil*[1]{\orgdiv{Centre for Global Health Research}, \orgname{Unity Health Toronto}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

### 2023-11-16 src/metrics.Rmd
Finish pccc func, work on CSMF acc
Fin csmf acc metric

>>>>

```{r}
calc_pccc <- function(actual, pred, k = 1, N = NULL) {

    # Calc N if not known
    N <- if (is.null(N)) length(unique(c(actual, pred))) else N

    # Calc frac of deaths in top k causes
    C <- sum(actual == pred) / len(actual)

    # Calc PCCC
    out <- (C - (k/N)) / (1 - (k/N))
    return(out)
}

calc_csmf_acc <- function(actual, pred, causes = NULL) {

    # Get all unique causes
    causes <- unique(c(actual, pred))

    # Get csmfs
    cases <- length(actual)
    csmf_true <- table(actual) / cases
    csmf_pred <- table(pred) / cases

    # Correct for missing causes in either actual or pred
    csmf_true <- vapply(
        causes,
        function(x) if (x %in% names(csmf_true)) csmf_true[x] else 0,
        FUN.VALUE = numeric(1)
    )
    csmf_pred <- vapply(
        causes,
        function(x) if (x %in% names(csmf_pred)) csmf_pred[x] else 0,
        FUN.VALUE = numeric(1)
    )

    # Calc csmf max error
    csmf_max_error <- 2 * (1 - min(csmf_true))

    # Calc csmf acc
    out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
    return(out)
}
```
